A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-05-30 elsfrontmatter.tex
Update on Overleaf.
adding citations
Shinichiro_30May

\begin{abstract}
Harmonization describes the process of calibrating Integrated Assessment Model
(IAM) results with a new source of historical emissions trajectories. To date,
harmonization has been performed separately by individual modeling teams through
the use of expert opinion and solicitation. As models and their results become
more complex in both regional and sectoral dimensions, an automated approach to
choosing harmonization methods becomes necessary. This work describes a novel
methodology for determining such harmonization methods and an open-source Python
code base for implementing the methodology. Results are shown for two example
scenarios using the MESSAGE-GLOBIOM IAM that satisfactorily harmonize over 98\%
of the total emissions trajectories. \cite{Dirac1953888}
\end{abstract}

>>>>

\begin{abstract}
Harmonization describes the process of calibrating Integrated Assessment Model
(IAM) GHG and air pollutants results with a new source of historical emissions trajectories. To date,
harmonization has been performed separately by individual modeling teams through
% * <sfujimori112256@gmail.com> 2017-05-24T19:26:26.142Z:
% 
% > harmonization has been performed separately by individual modeling teams 
% I think harmonization is not done. We just report the direct model outputs.
% 
% One of the ways to  make the background is that earlier IPCC scenarios (SRES and RCPs) did not document the harmonization method and far from transparent.
% 
% ^.
the use of expert opinion and solicitation. As models and their results become
more complex in both regional and sectoral dimensions, an automated approach to
choosing harmonization methods becomes necessary. This work describes a novel
% * <sfujimori112256@gmail.com> 2017-05-24T20:13:08.493Z:
% 
% > novel
% It would be better to stress how novel and useful.
% 
% ^.
methodology for determining such harmonization methods and an open-source Python
code base for implementing the methodology. Results are shown for two example
scenarios using the MESSAGE-GLOBIOM IAM that satisfactorily harmonize over 98\%
of the total emissions trajectories.
\end{abstract}

### 2017-05-30 intro.tex
Shinichiro_30May

Integrated Assessment Models (IAMs) are tools used to understand the complex
interactions between energy systems, economic systems, land use, the climate,
and air pollution, among other sectors . IAMs provide global projections of
systemic change by dividing the world into a number of representative regions,
the definition of which is distinct for each model. Results from IAMs are
integral in a number of international studies, which notably include projections
of climate and economic futures. Recently, flagship IAMs have developed
scenarios based on the Shared Socioeconomic Pathways (SSPs)
\cite{van_vuuren_energy_2017, kriegler_fossil-fueled_2017, calvin_ssp4:_2017,
  fujimori_ssp3:_2017, fricko_marker_2017} which model a variety of potential
global futures. The SSPs are used in analyses underpinning the Intergovernmental
Panel on Climate Change (IPCC) and the United Nations Framework Convention on
Climate Change (UNFCCC)'s Paris Agreement \TODO{cite}.

While IAMs are implemented in myriad ways, including simulation and
optimization, the core inputs, outputs, and purpose are similar across different
models. Modeling teams incorporate existing datasets of energy systems, world
development indicators, and emissions sources and concentrations, among other
data, in order to provide consistent historical trajectories of modeled
variables. The models then provide estimates of future trajectories of these
variables under various socioeconomic and technological assumptions as well as
proposed policy constraints, e.g., targets for future Greenhouse Gas (GHG)
emissions.

Future emissions pathways are of critical importance to both of global and local
governance concerns. For example, the United Nation's Sustainable Development
Goals (SDGs) \TODO{CITE} speak directly to the impacts of emissions in Goal 3
(Good Health and Well-Being) and Goal 13 (Climate Action). IAMs endogenously
calculate the trajectories many of the emissions species of import that impact
the progress towards these SDGs by modeling the individual technologies and
sectors that contribute towards the emissions of different air pollutants and
GHGs as well as various mitigation technologies (e.g., NOx and SOx scrubbers on
power plants).

@@

In order to incorporate the large variety of possible model results and given
relatively large increases in regional and sectoral dimensionality, an automated
process for determining harmonization methods is needed. The remainder of this
paper describes the methodology of the \code{aneris} code base, written in the
Python programming language, which implements such a system in Section
\ref{sec:meths}. The results of applying the automated harmonization mechanism
on two example IAM scenarios, one with emissions growth and another with
emissions mitigation, is presented in Section \ref{sec:results}. Finally, the
general effectiveness and potential future improvements on the automated
methodology is discussed in Section \ref{sec:future}.

>>>>

Integrated Assessment Models (IAMs) are tools used to understand the complex
interactions between energy systems, economic systems, land use, the climate,
and air pollution, among other sectors . IAMs provide global projections of
% * <sfujimori112256@gmail.com> 2017-05-24T20:16:51.179Z:
% 
% Here, Volker's paper seems well fit for the citation.
% http://onlinelibrary.wiley.com/doi/10.1002/wene.98/abstract
% 
% 
% ^.
systemic change by dividing the world into a number of representative regions (typically 10 to 30),
the definition of which is distinct for each model. Results from IAMs are
integral in a number of international studies, which notably include projections
of climate and economic futures. Recently, flagship IAMs have developed
scenarios based on the Shared Socioeconomic Pathways (SSPs)
\cite{van_vuuren_energy_2017, fricko_marker_2017, fujimori_ssp3:_2017,
  calvin_ssp4:_2017, kriegler_fossil-fueled_2017} which quantify a variety of
potential global futures. The SSPs are primarily designed to being used in analyses of broad climate research which includes earth system model (ESM) simulations, climate impact, adaptation climate mitigation studies. They consequently underpin the
Intergovernmental Panel on Climate Change (IPCC) across working groups and the United Nations
% * <sfujimori112256@gmail.com> 2017-05-24T20:32:22.989Z:
% 
% IPCC itself collects, reviews and summarizes papers. SSPs are officially independent activity from IPCC. So, I slightly changed the context. 
% 
% ^.
% * <sfujimori112256@gmail.com> 2017-05-24T20:37:11.995Z:
% 
% I think Paris agreement is not so relevant with SSPs so I removed.
% 
% ^.

While IAMs are implemented in myriad ways, including simulation and
optimization, the core inputs, outputs, and purpose are similar across different
models. Modeling teams incorporate existing datasets of energy systems, land use, economic, demographic and emissions sources and concentrations, among other
data, in order to provide consistent historical trajectories of modeled
variables. The models then provide estimates of future trajectories of these
variables under various socioeconomic and technological assumptions as well as
proposed policy constraints, e.g., targets for future Greenhouse Gas (GHG)
emissions.

Future emissions pathways are of critical importance to both of global and local
% * <sfujimori112256@gmail.com> 2017-05-24T20:47:32.377Z:
% 
% > Future emissions pathways are of critical importance to both of global and local
% > governance concerns. For example, the United Nation's Sustainable Development
% > Goals (SDGs) \TODO{CITE} speak directly to the impacts of emissions in Goal 3
% > (Good Health and Well-Being) and Goal 13 (Climate Action). IAMs endogenously
% > calculate the trajectories many of the emissions species of import that impact
% > the progress towards these SDGs by modeling the individual technologies and
% > sectors that contribute towards the emissions of different air pollutants and
% > GHGs as well as various mitigation technologies (e.g., NOx and SOx scrubbers on
% > power plants).
% I am not sure whether this paragraph is needed, because if we only discuss about SDGs, the emissions harmonization is not the necessity process for us essentially.
% 
% I would directly keen much more on the needs of harmonization and its importance. Then, the logic would be 
% 1) SSPs will be an basis for CMIP6 (Brian's scenarioMIP GMD paper citation)
% 2) CMIP6 uses different model outcomes (e.g. SSP1-26 IMAGE, SSP2-45 MESSAGE), which means we need somehow harmonized data set for at least base year.
% 3) However, current IAMs emissions inventory differ a lot, which is hardly acceptable for CMIP experiments.
% 4) 
% 
% 
% 
% ^.
governance concerns. For example, the United Nation's Sustainable Development
Goals (SDGs) \TODO{CITE} speak directly to the impacts of emissions in Goal 3
(Good Health and Well-Being) and Goal 13 (Climate Action). IAMs endogenously
calculate the trajectories many of the emissions species of import that impact
the progress towards these SDGs by modeling the individual technologies and
sectors that contribute towards the emissions of different air pollutants and
GHGs as well as various mitigation technologies (e.g., NOx and SOx scrubbers on
power plants).

@@

In order to incorporate the large variety of possible model results and given
% * <sfujimori112256@gmail.com> 2017-05-24T21:09:01.445Z:
% 
% I think it would be better to declare what metrics we are going to use to evaluate the methodology. In what case we can say this method succeeds or fails? That would be essentially the one of the highlight of the conclusion.
% 
% ^.
relatively large increases in regional and sectoral dimensionality, an automated
process for determining harmonization methods is needed. The remainder of this
% * <sfujimori112256@gmail.com> 2017-05-24T21:12:03.999Z:
% 
% > regional and sectoral dimensionality, an automated
% > process for determining harmonization methods is needed. The remainder of this
% 
% I suggest to add some explanations why detailed regional and sectoral harmonization is needed. As you mentioned, from RCPs sectoral and regional harmonization is needed. Meantime, ESM (or in this case we should say climate models) have been increasing the spatial resolution overtime and much more detailed representation become available, which essentially requires detailed information. The obvious example is AerChemMIP.
% 
% ^.
paper describes the methodology of the \code{aneris} code base \TODO{cite},
written in the Python programming language, which implements such a system in
Section \ref{sec:meths}. The results of applying the automated harmonization
mechanism on two example IAM scenarios, one with emissions growth and another
with emissions mitigation, is presented in Section \ref{sec:results}. Finally,
the general effectiveness and potential future improvements on the automated
methodology is discussed in Section \ref{sec:future}.
